Applying Renormalization Group Theory to the Square Well Liquid

### 2014-03-26 papers/thesis-roth/project.tex
added fig comparing SW and SW+RG Tested on elliot. Took 0:20.38.

% 1/k_B/T
\newcommand{\kt}{k_BT}

@@

The free energy density for each iteration is given by
\begin{equation}
  f_i(T,n) = f_{i-1}(T,n) + \delta f_i(T,n)\ .
\end{equation}
The total free energy density is obtained when one takes the
iterations to infinity and adds in the attractive component:
\begin{equation}
  f(T,n) = \lim_{i \to \infty} f_i(T,n) + f_{att}(T,n)\ .
\end{equation}
The initial free energy density, $f_0$ depends on the liquid model of study. For this work, I use the square well model:
\begin{equation}
  f_0(T,n) = f_{id}(T,n) + f_{HS}(T,n) + a_2^{SW}(T,n)\ ,
\end{equation}
where $a_2^{SW}(T,n)$ is the second-order term in a high-temperature expansion around $1/\kt$.~\cite{Gil-Villegas97}

@@

% \includegraphics[width=\columnwidth]{figs/combined-coexistence-plot}

>>>>

% 1/k_B/T
\newcommand{\kT}{k_BT}

@@

The free energy density for each iteration is given by
\begin{equation}
  f_i(T,n) = f_{i-1}(T,n) + \delta f_i(T,n)\ .
\end{equation}
The total free energy density is obtained when one takes the
iterations to infinity and adds in the attractive component:
\begin{equation}
  f(T,n) = \lim_{i \to \infty} f_i(T,n) + f_{att}(T,n)\ .
\end{equation}
The initial free energy density, $f_0$ depends on the liquid model of study. For this work, I use the square well model:
\begin{equation}
  f_0(T,n) = f_{id}(T,n) + f_{HS}(T,n) + \frac{a_2^{SW}(T,n)}{\kT}\ ,
\end{equation}
where $a_2^{SW}(T,n)$ is the second-order term in a high-temperature expansion around $1/\kT$.~\cite{Gil-Villegas97}

@@

When only including $f^{id}$ and $f^{HS}$ terms, SW and SW+RG match up
nicely. Including the $a_1^{SW}$ and $a_2$ terms doesn't work so
well...

\begin{figure}
  \begin{center}
  \includegraphics[width=\columnwidth]{figs/coexistance_SW}
  \end{center}
  \caption{Liquid-vapor coexistance for a square well liquid.}
  \label{fig:coexistance_SW}
\end{figure}

\begin{figure}
  \begin{center}
%  \includegraphics[width=\columnwidth]{figs/SW-RG-compare}
  \end{center}
  \caption{Comparison of free energy density for SW and SW+RG at low temperature}
  \label{fig:SW-RG-compare-loT}
\end{figure}

%% \begin{figure}
%%   \begin{center}
%%   \includegraphics[width=\columnwidth]{figs/}
%%   \end{center}  \caption{Comaprison of SW and RG near the critical point}
%%   \label{fig:SW-RG-compare-hiT}
%% \end{figure}
